A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.

### 2013-04-29 docs/Jesse/HeuerPaper/responseForReviewers.tex

\item \textcolor{red}{p. 21, just below (22): integrate $\rightarrow$ integrating}.  Corrected.
\item \textcolor{red}{p. 23, last formula: $r2 \rightarrow r_2$}.  Corrected.  There was also the same error in $r1$, which was also corrected.
\end{enumerate}

\textbf{Author remark: on the ratio curves for various values of $\epsilon$}

A few reasons why the curves in these figures are not guaranteed to lie on top of each other 
\begin{enumerate}
\item The proofs only guarantee that the ratio of $L^2$ to energy error is bounded by some constant independent of $\epsilon$.  Changing $\epsilon$ changes the problem, and the curves are not guaranteed to be similar.  The curves are not guaranteed even to be bounded away from zero; this is simply an observed phenomenon.  
\item The test norm used is mesh-dependent.  In this work, the constants placed in front of the $L^2$ portions of the test functions $v$ and $\tau$ are scaled by a mesh-dependent value, which takes two asymptotic values.  In the far-underresolved limit $h \gg \epsilon$, this value is $\epsilon$ for $\nor{v}_{L^2}$ and $1$ for $\nor{\tau}_{L^2}$ - these help guarantee that the optimal test functions do not contain boundary layers, which may introduce approximation error, which our analysis does not account for.  In the fully-resolved limit $h\approx \epsilon$, the values in front of $\nor{v}_{L^2}$ and $\nor{\tau}_{L^2}$ are $1$ and $\epsilon^{-1}$, respectively.  These are to help account for the fact that the $\nor{v}$ and $\nor{\tau}$ scale differently from $\nor{\grad v}$ and $\nor{\div \tau}$.

For the first example, the ratio curves each have a clear ``transition point", where the mesh introduces elements where $h \approx \epsilon$.  This transition occurs later as $\epsilon$ shrinks, simply due to the fact that it takes more degrees of freedom to introduce elements of size $\epsilon$ on a 1-irregular constrained mesh.

In the second example, a discontinuous boundary condition is approximated by a 20 term Fourier series.  As refinements are introduced, the problem itself changes due to the improved resolution of the boundary condition at the inflow (the ``moving target" issue).  This further complicates the matter, and the ratio is consequentially more ``messy"; however, it is still very close to 1 for every $\epsilon$ we tested.  
\item The scale can be misleading; we show the $y$-axis from $0$ to $2$.  In cases where there is \textit{not} a robust bound, these ratios scale with $\epsilon^{-1}$ - in other words, to show the ratios for $\epsilon$ up to $1e-4$, we would require a scale with $y \in [0,1e4]$, or a logarithmic scale from $0$ to $1e4$.  Under these scales, the curves would appear to lie more on top of one another.
\end{enumerate}

\closing{Best regards}

\bibliographystyle{plain}
\bibliography{paper}

\end{letter}
\end{document}
